Workflow and Software Documentation

### 2013-07-13 Workflow.Rnw
Scatterplot with two variables now a numbered section.
first draft of plot wrappers

A reasonable workflow is:
\begin{enumerate}
\item 
<<message=FALSE>>=
source("Econ-Growth-Resampling.R")
@
which, in turn, sources the file named \texttt{Econ-Growth_Functions2.R}.

\item
Execute the function called \function{genAllResampleData()}.

A typical call would be 
<<eval=FALSE>>=
genAllResampleData(method="wild", n=100)
@
\item Reload the data using one of the various ``load'' functions
from file \texttt{Econ-Growth-Functions2.R}:

@@

\begin{enumerate}
\item
A typical call for loadAllResampleData would be
<<eval=FALSE>>=
loadAllResampleData(modelType="cde", energyType="Q")
@
\item
Another example:
<<>>=
head(loadAllResampleData(model="sf", factor="K"), n=5)
@
\end{enumerate}
\end{enumerate}

\section{Ternary Plots}
\begin{enumerate}
\item
Plots of distributions of coefficients for the Cobb-Douglas 
with energy model can be made with \function{triPlot()} in 
file \texttt{Graphics.R}.  (Goofy labels here just to demonstrate what is possible.)
<<>>=
source("Graphics.R")
resData <- loadAllResampleData(modelType="cde", energyType="Q")
triPlot(subset(resData, method!="orig"), 
        gamma, alpha, beta,
        labels=c("gamma[1]", "alpha[2]", "sqrt(beta[3])"),
        n.grid=5,  aes_string="color=lambda", 
        size=3, alpha=.5 ) + 
     geom_point(data=subset(resData, method=="orig"), 
                color="red", alpha=1, size=3) +
     facet_wrap( ~ countryAbbrev )
@
Eventually, we can build a wrapper that loads the data and builds the plot with our favorite settings.
\end{enumerate}

\end{document}

>>>>

A reasonable workflow is:
\begin{enumerate}
\item 
<<message=FALSE>>=
source("Econ-Growth-Resampling.R")
@
which, in turn, sources the file named \texttt{Econ-Growth_Functions2.R}.
\item
<<>>=
source("Graphics.R")
@

\item
Execute the function called \function{genAllResampleData()} to cache the resampling data.

A typical call would be 
<<eval=FALSE>>=
genAllResampleData(method="wild", n=100)
@

\item Reload the data using one of the various ``load'' functions
from file \texttt{Econ-Growth-Functions2.R}:

@@

\begin{enumerate}
\item
A typical call for loadAllResampleData would be

<<>>=
head( loadAllResampleData(modelType="cde", energyType="Q"), n=3 )
@

\item
Other examples:
<<>>=
head( loadAllResampleData(model="sf", factor="K"), n=3 )
head( loadAllResampleData(model="linex", energyType = "Q"), n=3 )
head( loadAllResampleData(model="cese", energyType = "Q"), n=3 )
@
\end{enumerate}
\end{enumerate}

\section{Ternary Plots}
Plots of distributions of coefficients for the Cobb-Douglas-Energy
model can be made with \function{standardTriPlot()} in 
file \texttt{Graphics.R}.  
<<>>=
standardTriPlot( loadAllResampleData(modelType="cde", energyType="Q") ) +
  labs(title="Model = CDE; energy=Q")
@

\section{Scatterplots with two variables}

<<>>=
standardScatterPlot( loadAllResampleData(model="sf", factor="K"), 
                     aes(lambda, m) ) +
  labs(title="Model = sf; factor=K", x=expression(lambda))
@

<<>>=
standardScatterPlot( loadAllResampleData(model="linex", energyType = "Q"), 
                     aes(a_0, c_t) ) +
  labs(title="Model = linex; energy=Q", x=expression(a[0]), y=expression(c[t]))
@

<<>>=
standardScatterPlot( loadAllResampleData(model="cese", energyType = "Q"), 
                     aes(delta, rho) ) +
  labs(title="Model = cese; energy=Q", x=expression(delta), y=expression(rho))
@
\end{document}
